Disambiguating Monocular Depth Estimation with a Single Transient

### 2020-07-09 paper/eccv2020CR/sections/related.tex
compress figures, add related work, adjust author spelling

The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the transient measurement with the
output of a monocular depth estimator using a histogram matching technique.
While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an
image so that its histogram matches some pre-specified histogram (often derived
from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et
al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the
image pixels, yielding an exact histogram match. Morovic et
al.~\cite{Morovic2002} provide an efficient and precise method for fast
histogram matching which supports weighted pixel values. In the image
reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram
to form an image prior based on the Wasserstein distance for image denoising and
inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an
energy function that penalizes foreground segmentations with dissimilar
histograms. Caramazza et al.~\cite{caramazza2018neural} use a single
non-line-of-sight transient to recover the identity of a person hidden from
view. In a slightly different application area, Zhang et
al.~\cite{Zhang2017} train a neural network to produce realistically colorized
images given only a black-and-white image and a histogram of global color
information.

>>>>

The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
diffused across the entire scene instead of aimed at a single point, as with
proximity sensors. This unique configuration captures a measurement that closely
resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
reliable absolute depth estimation by combining the transient measurement with the
output of a monocular depth estimator using a histogram matching technique.
\edit{While other recent work also explored RGB-SPAD sensor
fusion~\cite{Lindell2018,sun2020spadnet},
the RGB image was primarily used to guide the denoising and upsampling of
measurements from a SPAD array.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an
image so that its histogram matches some pre-specified histogram (often derived
from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et
al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the
image pixels, yielding an exact histogram match. Morovic et
al.~\cite{Morovic2002} provide an efficient and precise method for fast
histogram matching which supports weighted pixel values. In the image
reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram
to form an image prior based on the Wasserstein distance for image denoising and
inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an
energy function that penalizes foreground segmentations with dissimilar
histograms. \edit{In the area of non-line-of-sight
imaging~\cite{faccio2020non,lindell2019wave,liu2020phasor,liu2019non,o2018confocal},
Caramazza et al.~\cite{caramazza2018neural} use a single
non-line-of-sight transient to recover the identity of a person hidden from
view.} In a slightly different application area, Zhang et
al.~\cite{Zhang2017} train a neural network to produce realistically colorized
images given only a black-and-white image and a histogram of global color
information.
